API design for machine learning: experiences from scikit-learn

### 2014-02-12 paper.tex
rewrite abstract to stress the general API rather than the lib
+ cite self

\sklearn is a machine learning library for the Python language.\footnote{\url{http://scikit-learn.org}}
It is designed to be simple and efficient, accessible to
non-experts, and reusable in various contexts. In this article, we present and
discuss the uniform application programming interface shared
by all learning and processing units in the library,
and the way it facilitates composition and reusability. We also comment on
implementation details specific to the Python ecosystem
and analyze potential obstacles faced by users and developers of the library.

>>>>

We describe a general, high-level application programming interface (API)
for machine learning and data mining.
This API, originally conceived for the Python library \sklearn
but now adopted by several machine learning packages,
is designed to be domain-independent and accessible
to workers in the wide variety of scientific and engineering fields
that employ machine learning.
We present and discuss how a small set of primitive concepts
facilititates composition of operations into complex workflows.\footnote{
  An earlier version of this paper was presented at the ECML~PKDD
  Workshop on Languages for Machine Learning \citep{buitinck2013ecml}.
}
